\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results }

### 2020-06-04 paper.tex
Cut long lines. Correct figures. Correct missing brackets. Compiles.

 The structural behavior of nanostructured materials  has  become a  great  topic  of global  interest,  where numerous  research has been done so far \cite{I1}. We found a great way to go for future technological  explorations,  countless  challenges and  that  open a range of possibilities to develop further  study  on these issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured material and an excellent candidate as a technological platform for different sensing applications \cite{I3, I4}, due to its easy manufacturing,  large surface area, high surface reactivity,  and moreover, its optical transduction capacity.  Photonic crystals are multilayer dielectric structures that have periodicity in the dielectric function along one direction \cite{I5}. It has numerous studies for high reflectivity and the ability to adjust  the photonic  prohibited  band (PBG)\cite{I6} , which leads to possible applications  such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the conventional manufacturing of PSi the desired result  is to obtain  homogeneous samples (same structural characteristics) from the  periphery  to the center  of the electrochemically  attacked area.  However, with an asymmetric anodizing configuration,  samples with a lateral gradient in terms of pore size and thickness of the porous layer are obtained \cite{I101}. In this configuration,  the face of the platinum  electrode (cathode)  is relatively maintained  perpendicular  to the surface of the Si substrate (anode) at one end of the cell, so that the distribution of the current within the electrolyte  solution varies depending on the distance  of the electrode due to the resistance of the electrolyte,  resulting  in a decrease in current density as the distance from the electrode increases \cite{I102, I103}. The result is a porous surface with different pore sizes ranging from a few nanometers  to pores on the order of a few micrometers  \cite{I104}. The dimensions of the pores obtained on the same chip can be controlled by adjusting the anodizing current and electrolyte concentration \cite{I11}. Currently, these types of samples have found their application relevant as optical band filters \cite{I12}, devices with a multidirectional photonic band (photonic bar codes) \cite{I13} and mainly as biosensors. In this way, the effect of different topographies (porosities in the same sample) on the culture / adhesion of certain cells \cite{I14} is studied, considerably reducing the number of samples and cost of the study. In addition, they are also very useful when a biomolecule size-exclusion technique is required allowing the identification and separation of these biological compounds \cite{I15}. Recent studies  have shown that  the  combination  of thermal  oxidation  and infiltration of TiO2   by ALD offers the  opportunity to manufacture  a high index of refraction  of contrast, visibly transparent GRIN optical elements from PSi absorbent structures \cite{I16}. A Despite previous research on the formation of porous silicon with GRIN, type p in manufacturing and characterization, there was no control of current densities, much less a model that  explained said lateral  gradient. In this work, we reported a gradient refractive index (GRIN) structure by varying the current density on the fabrication of porous silicon photonic structure. This current density values, depth, and porosity of the photonic structure were calculated from an electrostatic model for photonic crystals with a gradient refractive index (EMPCGRIN). Moreover, the theoretical and experimental studies were exhibited similar results.\\

@@

 \section{Theory}
 \subsection{Electrostatic Model for Photonic Crystals with Gradient Refraction Index (EMPCGRIN)}
The calculate  current density in a GRIN structure produced by an electrochemical attack on Si to produce Porous Si with a position-dependent porosity due to the distance to the counter electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b horizontal and c vertical. Here c considered as the height of the liquid, and the walls are insulating, but the bottom is completely covered with the sample, which act as good conductor. The electrode is a thin insulated cable with tip, which  a point  current source.
\begin{figure}[H]
	\centering
	\includegraphics[scale=.4]{../Images/celdan}
	\caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $ \sigma $ is the conductivity. This for the stationary case $ \bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived from the electric potential, $\vec {E} = - \bigtriangledown \varphi $.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the sample is a relatively good conductor, when connected to earth $ \varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
  \begin{equation}
\int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
  \begin{equation}
 q_{_{0}} = \dfrac{I}{4 \pi \sigma}
 \end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the tip of the electrode that is in the presence of a ground conductor plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0, y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of the liquid is also not conductive to $ (x, y, c) $, the normal current is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E} \cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By using the simplified prism geometry  can solve the problem using the theory of image loads. Each load has an image of the same sign and magnitude for each lateral insulating surface and the opposite sign change in the lower part of the conductive plane, as follows.
 \begin{figure}[H]
 \centering
 \includegraphics[scale=.6]{../Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a real charge in the corner of the cell with its charges ($ q $) images of the same sign in $ Z_0 $ and another charge image ($ -q $) with change of sign located below the conductor in position $ -Z_0 $. b) The upper face seen from above, a real load and its image loads in $ Z_0 $. c) All this formed a systems of a real load and its image loads produced by the cell walls and its other images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $) in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$ due to a reflection in $ (x, 0, z) $ y the image of the image in $\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then, these four charges are reflected on the other two surfaces and the eight new images are reflected on the original surface, etc., producing a periodic 2D rectangular network with unit cells of signs $ L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This entire network is reflected from the bottom with an opposite sign load (below the driver). Periodic copies separated by the vacuum in the $ xy $ plane whose area is being increased to achieve convergence. \\
\textbf {Problem considerations}: The problem is the potential, the field and the current produced by a periodic 2D network of a real load and all its images. The potential due to a periodic network is automatically found in the plane making a sum of 2D Fourier.

@@

 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)

@@

Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal network. It is written $ \phi (\vec{r}) = \displaystyle \sum _ {\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle \sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.

@@

 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)= -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta (z-z_0)

@@

Solving the homogeneous equation above and below $ z = z_0 $, using symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} = \phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And adjusting the singularity

@@

 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)

@@

For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2 \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A = L_x L_y $ is the unit cell area

@@

 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}

@@

 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} ) +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg( e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}

@@

 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)

@@

	\includegraphics[scale=.6]{../Images/celd1}
	\caption{\emph{Diagram shows that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $, the image is repeated vertically with the period $ L_z = 4c $}}

@@

In Fig. \ref{fig:Celda1} it is observed that there is a positive (real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a negative plate at $ 2c + z_0 $. Also, the image is repeated vertically with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11} would be rewritten, like this

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n} -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg) +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg( \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}} +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}  \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\\

@@

The constant K is chosen thus $ \phi (z = 0) $, substituting in Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are explicitly left with the geometric sum over $n$

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0} \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz) \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} - e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\

@@

\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc} \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber = K+\dfrac{16\pi q}{A} \\

@@

\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  + \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

I am sure it is correct. Then it goes to zero at $ z = 0 $. The term with c disappears if $ c \longrightarrow \infty $. The sum converges when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z \longrightarrow z_0 $. So it seems ready for calculation.

@@

\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

And the current density is for any $ z $, for our calculation we choose that $ z = 0 $

@@

\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  + \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0} -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

Integrating on the surface of the sample is obtained $I_{nm} =\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$

@@

\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\ I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)

@@

Using the factor of the reciprocal vector in this way $ \vec {G} = \bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in \ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n and m, only the constant term taxpayer to the integrated current

@@

One of the methods used for the analysis of photonic crystal structures is the transfer matrix method. We use it to investigate the reflectance of light in a one-dimensional photonic crystal. The electric and magnetic fields within the layers are shown as $E_m$ and $H_m$. Then we can specify the electric and magnetic fields in the air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:

@@

Where N is the total number of layers including the cavity layer and $ M_j $ is the matrix characteristic of the layer $ j $ specified by:

@@

where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} - ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $ is the thickness of the layer, and $ \theta_j $ is the angle of refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $ for layer j is defined as:

@@

where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space permeability, respectively. The transfer matrix of all the photonic crystal is given by:

@@

We can write the reflection and transmission coefficients in a one-dimensional photonic crystal nanocavity as:

@@

r=\frac{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m) -(m_{21}+m_{22}\eta_m)}

@@

where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet layers, respectively (as defined in equations \ref{Eq:Mt1} or \ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of the entire photonic crystal nanocavity is given by:

@@

	\includegraphics[scale=0.6]{../Images/DE1}

>>>>

The structural behavior of nanostructured materials  has  become a
great  topic  of global  interest,  where numerous  research has been
done so far \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PSi the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PSi
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

\section{Theory}
\subsection{Electrostatic Model for Photonic Crystals with Gradient
  Refraction Index (EMPCGRIN)}

The calculate  current density in a GRIN structure produced by an
electrochemical attack on Si to produce Porous Si with a
position-dependent porosity due to the distance to the counter
electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b
horizontal and c vertical. Here c considered as the height of the
liquid, and the walls are insulating, but the bottom is completely
covered with the sample, which act as good conductor. The electrode is
a thin insulated cable with tip, which  a point  current source.
\begin{figure}[H]
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
\sigma $ is the conductivity. This for the stationary case $
\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
from the electric potential, $\vec {E} = - \bigtriangledown \varphi
$.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
sample is a relatively good conductor, when connected to earth $
\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
\begin{equation}
  \int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
\begin{equation}
  q_{_{0}} = \dfrac{I}{4 \pi \sigma}
\end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
tip of the electrode that is in the presence of a ground conductor
plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
the liquid is also not conductive to $ (x, y, c) $, the normal current
is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
\cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}[H]
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

From Fig. \ref{fig:T1} we assume that if i put a real charge ($ q $)
in at $\vec{r}_0= (x_0, y_0, z_0)$, in the corner of the electrolytic
box it induces images at $\vec{r}_1= (-x_0, y_0, z_0)$ due to a
reflection in $ (0, y, z) $, images in  $\vec{r}_2= (-x_0, -y_0, z_0)$
due to a reflection in $ (x, 0, z) $ y the image of the image in
$\vec{r}_3= (x_0, -y_0, z_0)$  for  $\vec{r}_j$, $(j=0,1,2,3)$. Then,
these four charges are reflected on the other two surfaces and the
eight new images are reflected on the original surface, etc.,
producing a periodic 2D rectangular network with unit cells of signs $
L_x = 2a $, $ L_y = 2b $ and with a base of 4 equal charges. This
entire network is reflected from the bottom with an opposite sign load
(below the driver). Periodic copies separated by the vacuum in the $
xy $ plane whose area is being increased to achieve convergence.

\textbf {Problem considerations}: The problem is the potential, the
field and the current produced by a periodic 2D network of a real load
and all its images. The potential due to a periodic network is
automatically found in the plane making a sum of 2D Fourier.

@@

 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)

@@

Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
Poisson equation $ \bigtriangledown^2 \phi = -4 \pi \displaystyle
\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.

@@

 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
   (z-z_0)

@@

Solving the homogeneous equation above and below $ z = z_0 $, using
symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
adjusting the singularity

@@

 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)

@@

For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
L_x L_y $ is the unit cell area

@@

 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}

@@

 \phi(\vec{r}) = -\dfrac{8\pi q}{A} \bigg((\abs{z-z_0}-\abs{z+z_0} )
    +\dfrac{8\pi q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \bigg(
    e^{- G \abs{z-z_0}} -e^{- G \abs{z+z_0}}  \bigg) \cos(G_x x_0)
    \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}

@@

 \phi(\vec{r}) = -\dfrac{16\pi q}{A} \bigg( z
     +\displaystyle\sum_{\vec{G}} \dfrac{1}{G} \sinh(G z)  \cos(G_x
     x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}} \bigg)

@@

  \includegraphics[scale=.6]{Images/celd1}
  \caption{\emph{Diagram shows that there is a positive (real) plane $
      z_0 $, a negative image at $ -z_0 $ below the conductor ($ z = 0
      $) and its images are a positive plate at $ 2c-z_0 $ and a
      negative plate at $ 2c + z_0 $, the image is repeated vertically
      with the period $ L_z = 4c $}}

@@

In Fig. \ref{fig:Celda1} it is observed that there is a positive
(real) plane $ z_0 $, a negative image at $ -z_0 $ below the conductor
($ z = 0 $) and its images are a positive plate at $ 2c-z_0 $ and a
negative plate at $ 2c + z_0 $. Also, the image is repeated vertically
with the period $ L_z = 4c $. Therefore, the equation \ref{Eq:EC11}
would be rewritten, like this

@@

 \nonumber\phi(\vec{r}) = K+\dfrac{8\pi q}{A} \displaystyle\sum_{n}
   -\bigg(\abs{z-z_0-nL_z}-\abs{z+z_0-nL_z}-\abs{z+2c+z_0-nL_z}+\abs{z-2c-z_0-nL_z}\bigg)
   +\\ \nonumber \dfrac{1}{G}\displaystyle\sum_{\vec{G}}\bigg(
   \displaystyle\sum_{n} \bigg( e^{-\abs{z-z_0-nL_z}}
   +e^{-\abs{z+z_0-nL_z}}-e^{-\abs{z+2c+z_0-nL_z}}-e^{-\abs{z-2c-z_0-nL_z}}
   \bigg)\bigg)\cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot
   \vec{r}}\\

@@

The constant K is chosen thus $ \phi (z = 0) $, substituting in
Eq. (\ref {Eq:EC1}) and after factoring $ e^{- nGL_Z} $ we are
explicitly left with the geometric sum over $n$

@@

    \nonumber\phi(\vec{r}) = K+\dfrac{16\pi q}{A} \bigg(z+z_0  +
    \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-Gz_0}
    \sinh(Gz)+e^{-Gz_0(2c_z)} \sinh(Gz_0) -e^{-2Gc} \sinh(Gz)
    \sinh(Gz_0) \\ \nonumber \dfrac{1+\cosh(2Gc)}{\sinh(2Gc)} -
    e^{-2Gc}\cosh(2Gc) \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
    y_0) e^{i \vec{G} \cdot \vec{r}}   \bigg)\\

@@

\nonumber\phi(x, y, 0) = K+\dfrac{16\pi q}{A} \bigg(z_0  +
   \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \bigg(e^{-2Gc}
   \sinh(Gz_0)-e^{-2Gc} \sinh(Gz_0)   \bigg) \cos(G_x x_0) \cos(G_y
   y_0) e^{i \vec{G} \cdot \vec{r}}\bigg) =\\ \nonumber =
   K+\dfrac{16\pi q}{A} \\

@@

\nonumber\phi(\vec{r}) = \dfrac{16\pi q}{A}\bigg( z  +
   \displaystyle\sum_{\vec{G}}\dfrac{\sinh(Gz_0)}{G} \bigg(e^{-Gz_0}
   -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg)
   \cos(G_x x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

I am sure it is correct. Then it goes to zero at $ z = 0 $. The term
with c disappears if $ c \longrightarrow \infty $. The sum converges
when $ G \longrightarrow \infty $ if $ z <z_0 <c $ and diverges to $ z
\longrightarrow z_0 $. So it seems ready for calculation.

@@

\nonumber E_\perp = -\dfrac{16\pi q}{A}\bigg( 1  +
  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz)\bigg(e^{-Gz_0}
  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

And the current density is for any $ z $, for our calculation we
choose that $ z = 0 $

@@

\nonumber J_\perp = -\dfrac{I}{ab}\bigg( 1  +
  \displaystyle\sum_{\vec{G}}\dfrac{1}{G} \cosh(Gz_0) \bigg(e^{-Gz_0}
  -e^{-3Gc} \dfrac{\cosh(Gc)\sinh(Gz_0)}{\sinh(2Gc)}   \bigg) \cos(G_x
  x_0) \cos(G_y y_0) e^{i \vec{G} \cdot \vec{r}}  \bigg)\\

@@

Integrating on the surface of the sample is obtained $I_{nm}
=\int^{a}_0 dx \int^{b}_0 dy \ \ e^{i\vec{G}\vec{r}}$

@@

\nonumber I_{nm}=\dfrac{1}{G_x G_y} (e^{-iG_xa}-1) (e^{-G_y b}-1) \\
  I_{nm}=\dfrac{ab}{nm \pi^2} ((-1)^n-1-1)(-(1)^m-1-1)

@@

Using the factor of the reciprocal vector in this way $ \vec {G} =
\bigg (\dfrac{\pi}{a} n, \dfrac{\pi}{b} m \bigg) $,
however, as all the coefficients of $ e^{- i \vec{G} \vec{r}} $ in
\ref{Eq:J} they are even in $ \vec{G} $ and the integral is odd in n
and m, only the constant term taxpayer to the integrated current

@@

One of the methods used for the analysis of photonic crystal
structures is the transfer matrix method. We use it to investigate the
reflectance of light in a one-dimensional photonic crystal. The
electric and magnetic fields within the layers are shown as $E_m$ and
$H_m$. Then we can specify the electric and magnetic fields in the
air, $ E_0 $ and $ H_0 $, by solving the following matrix equation:

@@

Where N is the total number of layers including the cavity layer and $
M_j $ is the matrix characteristic of the layer $ j $ specified by:

@@

where $ \lambda $ is the wavelength, $ \tilde{n}_{_{j}} = n_{j} -
ik_{_{j}}$ is the complex refractive index (CRI) of the layer, $ d_j $
is the thickness of the layer, and $ \theta_j $ is the angle of
refraction of light in the $ j $ layer. The parameter $ \eta_ {j} $
for layer j is defined as:

@@

where $ \epsilon_0 $ and $ \mu_0 $ are permittivity and free space
permeability, respectively. The transfer matrix of all the photonic
crystal is given by:

@@

We can write the reflection and transmission coefficients in a
one-dimensional photonic crystal nanocavity as:

@@

r=\frac{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}{\eta_0(m_{11}m_{12}\eta_m)
  -(m_{21}+m_{22}\eta_m)}

@@

where $ \eta_0 $ and $ \eta_m $ are parameters for air and outlet
layers, respectively (as defined in equations \ref{Eq:Mt1} or
\ref{Eq:Mt2}). Furthermore, the reflectivity R and transmittance T of
the entire photonic crystal nanocavity is given by:

@@

  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
